\documentclass[a4paper,11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{cv}

\name{J\'onathan Heras}
\info{Address: & Department of Mathematics and Computer Science, University of La Rioja, Spain\\
      Phone: & +34 941299455\\
      Email: & jonathan.heras@unirioja.es\\
      WWW: & www.unirioja.es/cu/joheras}
 
\bibliography{biblio}
 
\addtocategory{papers}{fKenzo-JSC,fKenzo-RSME,imagenA,ACM11,HCMS13,HK13EPTCS,KSH14,HK14,PDHR14,RSME14}
\addtocategory{papers}{AAECC15,BIB15,BMC15,BIB15B,JOST16,CHB16,JSDOGH16,CMPB16,
CCIS17,CMPB17,CBM17,BMC18,CALL18,TOCE18,IJEE19,NCAA19,SOCO19,CBM19,BMC19,IEEEA20,CEA20,CMPB20,CMPBEsferoides,Mathematics2021,PR21,CBM21Motilidad,CBM21Afshin,JImaging,Frontiers2021,PRAG2022,Frontiers2022,HA4M,Zubia22,DMAE22,JUCS23,SueAnn23,Zaragoza23,Afhsin23,SOCO23,NeuroComputing23}
\addtocategory{papers}{SEPLN23b,AIROGS,SEPLN24b,SEPLN24a,FrontiersPlantScience24,Marion,JCS24,BSPC2025,MariaCIBM25,madadi2025justraigs,SEPLN25,Neurocomp25}
\addtocategory{chapters}{CMirian10}
\addtocategory{conferences}{ELS08,EACA08,MKM08,ELS09,MATHUI09,OpenMath09,MKM09,cme09,HardSoft10,EACA10}
\addtocategory{conferences}{MKM10,LOPSTR10,EACA12-1,EACA12-2,CTIC12,CICM12,
Eurocast11,CICM11-1,CICM11-2,CAAT11}
\addtocategory{conferences}{CICM13-1,CICM13-2,ARW13,ACA13,LPAR-19,ACL2-14,ICLP14
,Coq14,PROLE14,AISC14,galway,Bioimaging2016, 
CAEPIA16,EUROCAST17,CICM2017,MedicalWorkshop2017,JENUI2018,DCAI2018-1}
\addtocategory{conferences}{DCAI2018-2,CAEPIA18,EUROCAST19Angela, 
EUROCAST19Manuel, EUROCAST19Adrian, ISSAC-19,JENUI2019,ECAI2020,
DAS2020,ECPA2021,JENUI2020,JENUI2021,CAEPIA2021a,CAEPIA2021b,CAEPIA2021c,CAEPIA2021d,CAEPIA2021e,
IBPRIA22,Jared22,EUROCAST2022,IWINAC2022,DAS2022Maria,DAS2022Gonzalo,DCAI2022Maria,JENUI2022}
\addtocategory{conferences}{SEAE21,ECMLPKDD21,CVPPA21,SEEIMC21,ECCMID21,EUROCAST2022post,ECPA2023a,ECPA2023b,OLA2023a,OLA2023b,ASELE2023,CIVILCOMP2023,IBPRIA23,SEPLN23a,SEPLN23c, CVPPA23a,Iberlef2023,IEEEDataScience,EUROCAST24, MMAC, LRECColing2024, CAEPIA2024a,CAEPIA2024b,CAEPIA2024c,CAEPIA2024d,CAEPIA2024e,CAEPIA2024f,ISBI2024,IWSDS25,DMHW25,
IWANN25,ASEBIR25,SEPLN25-LSE}
\addtocategory{posters}{microscopy,bioimaging,neuroscience,neurociencia,om22,
arw-poster,neubias-poster1,neubias-poster2,neubias-poster3,neubias-poster4,
neubias-poster5}
\addtocategory{phd}{herasphd}
\addtocategory{book-ed}{ARW13_proc,EACA16_proc}

\begin{document}
\maketitle
 
\section{Education and Qualifications}
\begin{tabular}{lll}
2007 & BSc on Mathematics  & University of La Rioja (Spain)\\
2007 & BSc on Computer Science & University of La Rioja (Spain)\\
2008 & MSc on Mathematics & University of Zaragoza (Spain)\\
2011 & PhD on Mathematics/Computer Science & University of La Rioja (Spain)\\
\end{tabular}

\section{Positions}

\begin{tabular}{ll}

September 2015 - Present & Lecturer at the Department of Mathematics and\\
& Computer Science, University of La Rioja.\\

October 2015 - December 2015 & Software Developer at the company 
Formavolución.\\

August 2014 - September 2015 & Postdoctoral Research Assistant at the Department of\\
&Mathematics and Computer Science, University of La Rioja.\\
&PI: C\'esar Dom\'inguez.\\

August 2012 - June 2014 & Postdoctoral Research Assistant at the School of Computing,\\
&University of Dundee. PI: E. Komendantskaya.\\

January 2012 - July 2012 & Postdoctoral Research Assistant at the Department of\\
&Mathematics and Computer Science, University of La Rioja.\\
&PI: Thierry Coquand.\\

September 2008 - December 2011 & PhD scholarship at the Department of Mathematics and\\
&Computer Science, University of La Rioja. \\

September 2007 - August 2008 & Research Assistant at the Department of Mathematics and\\
&Computer Science, University of La Rioja. PI: Julio Rubio.\\


% September 2014 - present & & Postdoctoral Research Assistant at the Department of\\
%&Mathematics and Computer Science, University of La Rioja.\\

\end{tabular}

\begin{publications}
\printbib{papers}
\printbib{chapters}
\printbib{conferences}
\printbib{posters}
\printbib{phd}
\printbib{book-ed}
\end{publications}

\section{PhD Supervision}

\begin{enumerate}
 \item A. Inés (2022). ``Simplifying the usage and construction of deep image classification models''. PhD thesis. University of La Rioja. Co-supervised with Julio Rubio. 
 \item M. García-Domínguez (2022). ``
Democratizing Deep Learning methods by means of AutoML tools''. PhD thesis. University of La Rioja. Co-supervised with César Domínguez. 
 \item A. Casado-García (2023). ``Deep Detection and Segmentation Models for Plant Physiology and Precision Agriculture''. PhD thesis. University of La Rioja. Co-supervised with Vico Pascual. 
\end{enumerate}


\section{Participation in Grants}

\begin{enumerate}

\item \emph{Corpus Oral de Referencia del Español en Contacto. Fase II: Lenguas minoritarias}. Funded by Ministerio de Ciencia e Innovación. PI: Sara Gómez. 2024--2028.

\item \emph{LSEAvatar}. Funded by Indra y Fundación Universia. PI: Jónathan Heras. 2024--2025.
\item \emph{SegDAn: Motor para la segmentación semántica, la segmentación de instancias y la detección de anomalías en imágenes como soporte para la transformación digital de la industria}. Funded by Agencia de Desarrollo Económico de La Rioja. PI: César Domínguez. 2024--2026.
\item \emph{PrevenIA: un chabot para la prevención del suicidio y otros trastornos de salud mental}. Funded by 2023 strategies of the Spanish Ministry of Health, which were approved in the CISNS on June 23, 2023, to support the implementation of the Mental Health Action Plan. PI: César Domgínguez. 2023-2024.
\item \emph{Systematic manipulation of tau protein aggregation: bridging biochemical and pathological properties}. Funded by Canadian Institutes of Health Research. PI: Sue-Ann Mok. 2023--2028.
\item \emph{Inteligencia artificial para el procesamiento de imágenes 
y textos: aplicaciones para el bien social.} Funded by Gobierno de La Rioja. PI: Gadea Mata. 2024--2026.
 \item \emph{Aspectos Matematicos Del Procesamiento De Imagenes Biomedicas: Metodos Topologicos Y De Ciencia De Datos}. Funded by 
Ministerio de Ciencia e Innovación. 
PIs: C. Domínguez and V. Pascual. 2021--2024.
 \item \emph{HOLMS: Técnicas
Avanzadas de Análisis de Imágenes para Categorización y Extracción de 
Información en Documentos}. Funded by 
Ministerio de Ciencia, Innovación y Universidades. 
PI: C. Domínguez. 2018--2021.
 \item \emph{Álgebra Computacional: formalización y aplicaciones a la 
fiabilidad de redes y al procesamiento de imágenes biomédicas}. Funded by 
Ministerio de Economía y Competitividad. 
PIs: E. Sáenz-de-Cabezón and V. Pascual. 2018--2020.
 \item \emph{CLODE: motor para la clasificación, localización y detección de 
objetos en imágenes y vídeos para la Industria 4.0}. Funded by an ADER grant. 
PI: C\'esar Dom\'inguez. 2018--2020.
 \item \emph{Formalization of Mathematics: applications to symbolic computation 
and computer algebra}. Funded by Ministerio de Econom\'ia y Competitividad. PI: 
Julio Rubio. 2015--2017.
 \item \emph{DIGIBAC: Desarrollo de métodos automatizados para el análisis de 
imágenes digitales de patrones de electroforesis de bacterias}. Funded by an 
ADER grant. PI: C\'esar Dom\'inguez. 2014--2016.
 \item \emph{Machine Learning for ACL2}. Funded by SICSA Proof of Concept 
programme.  PI: J\'onathan Heras. 2013--2014.
 \item \emph{Coalgebraic Logic Programming for Type Inference: parallelism and 
corecursion for a new generation of programming languages}. Funded by EPSRC. 
       PI: Ekaterina Komendantskaya. 2013--2016.
 \item \emph{Machine-learning coalgebraic automated proofs}. Funded by EPSRC 
First Grant scheme. PI: Ekaterina Komendantskaya. 2011--2013.
\item \emph{Formath: Formalization of Mathematics}. Funded by European Union. 
PI: Thierry Coquand. 2010--2013.
 \item \emph{Mathematical Knowledge Management: Algebraic Topology and Logic 
cases}. Funded by Ministerio de Ciencia e Innovaci\'on. PI: Julio Rubio. 
2009--2012.
 \item \emph{Asistentes para la creaci\'on de aplicaciones cliente de sistemas 
de c\'alculo simb\'olico}. Funded by Comunidad Aut\'onoma de La Rioja. PI: Vico 
Pascual. 2008--2010.
 \item \emph{Computer Algebra systems: new developments in Algebraic Topology 
and reliability}. Funded by Comunidad Aut\'onoma de La Rioja. PI: Julio Rubio. 
2007--2008.
\end{enumerate}

\section{Awards}

\begin{itemize}
  \item 
Award in the \href{https://caepia20-21.uma.es/}{CAEPIA conference} for the paper ``Prediction of Epiretinal Membrane from Retinal Fundus Images using Deep Learning''. 2021.
  \item 
\href{
http://www.computingreviews.com/recommend/bestof/notableitems.cfm?bestYear=2014}
{\emph{Notable Article in Computing 2014}} for the paper ``A certified reduction 
strategy for homological image processing''. 2015.
 \item Awarded a diploma for one of the best PhD dissertations written at the 
University of La Rioja in academic year 2010/11. 2013.  
 \item Best programming pearl award for the paper \emph{Homological processing 
of biomedical images} at the 1st workshop of Industrial Applications of Computer 
Algebra (AICA'11). 2011.
\item Received PhD scholarship at the Department of Mathematics and Computer 
Science, University of La Rioja. 2008--2011.
\end{itemize}

\section{Contracts with companies}

\begin{itemize}
  \item Diagnosing diseases from images from retinal fundus. Company: OPTRetina. 2021. Principal Investigator.
  \item Predicting the production using temporal series. Company: Grupo Empresarial Palacios Alimentación. 2021. Collaborator. 
  \item Detection of anomalous objects in industrial plants. Company: SpectralGeo. 2020--2023. Principal Investigator. 
  \item Digitizing the musical archive of Santo Domingo's Cathedral. Company: Instituto de Estudios Riojanos. 2020--2022. Principal Investigator. 
\end{itemize}

\section{Teaching}

\begin{itemize}
\item Lecturer of the module ``Aprendizaje Profundo'' (MSc course). 
Department of Mathematics and Computer Science, University of La Rioja. From Spring 2020 to present. 
\item Lecturer of the module ``Inteligencia Artificial'' (BSc course). 
Department of Mathematics and Computer Science, University of La Rioja. From Spring 2016 to present. 
\item Lecturer of the module ``Programación Orientada a Objetos'' (BSc course). 
Department of Mathematics and Computer Science, University of La Rioja. From Autumn 
2016 to 2022.
 \item Lecturer of the module ``Tecnología de la Programación'' (BSc course). 
Department of Mathematics and Computer Science, University of La Rioja. From Spring 
2016 to Spring 2017.
 \item Lecturer of the module ``Herramientas TIC para docentes''. Diploma de 
Extensión Universitaria en Formación Pedagógica y Didáctica, University of La 
Rioja. Autumn 2015, Autumn 2016, Autumn 2017.
 \item Lecturer of the module ``Taller Informática I''. Universidad de la 
Experiencia, University of La Rioja. Autumn 2015, Autumn 2016, Autumn 2017.
 \item Lecturer of the module ``Desarrollo de Aplicaciones Web'' (MSc course). 
Department of Mathematics and Computer Science, University of La Rioja. From Autumn 
2015 to Autumn 2019.
 \item Lecturer of the module ``Algorithms and Artificial Intelligence'' (BSc course). University of Dundee. Spring 2014.
  \item Lecturer of the module ``Introduction to Programming'' (BSc course). University of Dundee. Autumn 2013.
   \item Lab assistant of the module ``Architecture Fundamentals and Unix'' (BSc course). School of Computing, University of Dundee. Autumn 2012.
 \item Lab assistant of the module ``Metodolog\'ia de la Programaci\'on'' (BSc course). Department of Mathematics and Computer Science, University of La Rioja. Autumn 2011. 

\end{itemize}

\section{Academic visits}

\begin{itemize}
 \item Chalmers University. Goteborg, Sweden. May 2012.
  \item University of Seville. Seville, Spain. July 2011.
  \item INRIA-Sophia institure. Sophia, France, September 2010.
   \item University of Seville. Seville, Spain. February 2010.
    \item German Research Center for Artificial Intelligence. Saarbrucken, Germany. October 2009.
\end{itemize}

\section{Further Academic Service}

\begin{itemize}
 \item Organisation Committee membership: \href{http://www.unirioja.es/dptos/dmc/MAP2010/}{MAP 2010}, \href{http://www.computing.dundee.ac.uk/staff/katya/arw13/}{ARW13}, \href{http://staff.computing.dundee.ac.uk/katya/spls/index.html}{SPLS14}, \href{http://www.unirioja.es/dptos/dmc/EACA2016/index.shtml}{EACA 2016}.
 \item Programme Committee membership: \href{http://www.cicm-conference.org/2013/cicm.php}{CICM'13}, \href{http://cicm-conference.org/2014/cicm.php}{CICM'14}, \href{https://coq.inria.fr/coq-workshop/2016}{Coq'16}, \href{http://www.ipac.icc-conference.org/index.html}{IPAC'16}.
 \item Reviewer: \href{http://ilp13.cos.ufrj.br/}{ILP'13}, 
\href{
http://www.springer.com/computer/theoretical+computer+science/journal/10817}{
Journal of Automated Reasoning}, 
\href{http://rspa.royalsocietypublishing.org/}{Proceedings A},
\href{http://www.journals.elsevier.com/journal-of-symbolic-computation}{Journal 
of Symbolic Computation}, \href{http://link.springer.com/journal/165}{Formal 
Aspects of Computing}, 
\href{https://www.journals.elsevier.com/journal-of-immunological-methods}{
Journal of Immunological Methods}, 
\href{https://link.springer.com/journal/10528}{Biochemical Genetics}, 
\href{https://www.journals.elsevier.com/journal-of-advanced-research}{Journal of 
Advanced Research}, \href{https://www.mdpi.com/journal/applsci}{Applied 
Sciences}, \href{https://www.journals.elsevier.com/computers-in-biology-and-medicine}{Computers in Biology and Medicine}, \href{https://www.sciencedirect.com/journal/information-processing-in-agriculture}{Information Processing in Agriculture}, 
\href{https://onlinelibrary.wiley.com/journal/15410420?campaign=UPDCOEph&tabActivePane=}{Biometrics}, \href{https://www.mdpi.com/journal/electronics}{Electronics} (member of the reviewer board), \href{https://www.mdpi.com/journal/energies}{Energies}, \href{https://peerj.com/}{PeerJ}, \href{https://www.journals.elsevier.com/computers-and-electrical-engineering}{Computers and Electronical Engineering}, \href{https://www.journals.elsevier.com/softwarex}{SoftwareX}, \href{https://www.nature.com/ncomms/}{Nature Communications}, \href{https://www.springer.com/journal/12652}{Journal of Ambient Intelligence and Humanized Computing}, \href{https://www.frontiersin.org/journals/psychology}{Frontiers in Psychology}, \href{https://cis.ieee.org/publications/t-emerging-topics-in-ci}{IEEE Transactions on Emerging Topics in Computational Intelligence}, \href{https://www.frontiersin.org/journals/signal-processing}{Frontiers in Signal Processing},
\href{https://ieeeaccess.ieee.org/}{IEEE Access}. 

\end{itemize}

\section{Software}

\begin{itemize}
 \item \href{http://www.unirioja.es/cu/joheras/fKenzo/}{fKenzo}: A system for 
computing and reasoning in Algebraic Topology. 2011.
 \item \href{http://staff.computing.dundee.ac.uk/katya/ML4PG/}{ML4PG}: Machine 
Learning for Proof General. 2012--2014.
 \item \href{http://staff.computing.dundee.ac.uk/jheras/acl2ml/}{ACL2(ml)}: 
Machine Learning for ACL2. 2013--2014.
 \item \href{https://sourceforge.net/projects/gelj/}{GelJ}: a Java program for 
the analysis of DNA gel fingerprints images. 2015--2016.
 \item 
\href{https://sourceforge.net/projects/wekabiosimilarity/}{WekaBioSimilarity}: 
binary measures in Weka. 2016.
 \item \href{https://github.com/joheras/IJ-OpenCV}{IJ-OpenCV}: a Java library 
connecting ImageJ and OpenCV. 2016.
 \item \href{https://sourceforge.net/projects/antibiogramj/}{AntibiogramJ}: a 
Java program for reading antibiogram images. 2016.
 \item 
\href{https://joheras.github.io/DetectionEvaluationJ/}{DetectionEvaluationJ}: 
an ImageJ plugin that has been designed to evaluate the performance of object 
detection algorithms using several metrics. 2016.
 \item 
\href{http://decofungi.unirioja.es:8000}{DecoFungi}: 
a web application for measuring dye decolorisation from fungal strains. 2017.
\item 
\href{https://github.com/joheras/clodsa}{CLoDSA}: 
an open-source image augmentation library for object classification, localization, detection, semantic segmentation and instance segmentation. 2019.
\end{itemize}





\end{document}
